#INFO498F Survey 

```{r, echo=FALSE, message=FALSE}
library(plotly)
library(dplyr)

#Read in the functions in other files
source("scripts/Chart1.R")
source("scripts/Chart2.R")
source("scripts/summary.R")
source("README.md")

#Read in the data
summary_information <- info_summary(data)
```

There are a total of `r summary_information$num` students in class; there are `r summary_information$numFreshmen` freshmen, `r summary_information$numSophomore` sophomores, `r summary_information$numJunior` juniors, and `r summary_information$numSenior` seniors. `r summary_information$numWindows` of the students are Windows users, and `r summary_information$numMac` of the students are Mac users.

Here is a scatter plot showing the classes of students grouped by the
number of countries they have visited before:

```{r, echo=FALSE, message=FALSE}
#Pass the data to render chart 1
class_travel(data)
```

Here is a bar chart showing the classes of students grouped by saying yes, no, N/A, or
maybe when asked if they wanted to apply to informatics:

```{r, echo=FALSE, message=FALSE}
#Pass the data to render chart 2
class_major(data)
```